### 2018-09-10 ICRA19/covControl.tex
added lead figure, and kilobot angle of repose section

\subsection{Hardware experiment: kilobot angle of repose}
In this section we vary the force and approach angle to shape a swarm with a characteristic angle of repose.

\textcolor{red}{TODO: Shiva will insert the kilobot images and a couple of sentences, and a couple of sentences about kilobots}

>>>>

\subsection{Hardware experiment: kilobot angle of repose}

In this section we vary the force and approach angle to shape a swarm of Kilobots \cite{rubenstein2014programmable} with a characteristic angle of repose. Kilobot is a three centimeter low cost robot that has light sensor. In our experiments, these robots were programmed to go toward the brightest light in the room. The experimental setup is shown in Fig. \ref{fig:SetUp}. Figure \ref{fig:kilobotAngle} shows angle of repose of the Kilobots with three different angles of the pink rod when the rod has 0$^\circ$, 22.5$^\circ$ and 45$^\circ$. The green lines show the triangle that the robots pile up. The cyan star is the center of mass of the rod, and mean position and variance of the robots are shown with a red star and red ellipse.
\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{SetUp.pdf}
\end{center}
\caption{\label{fig:SetUp}
The platform where we control Kilobots with lights.
}
\end{figure}

\begin{figure}
\begin{center}
	\includegraphics[width=\columnwidth]{KilobotAngleThreeAngles.pdf}
\end{center}
\caption{\label{fig:kilobotAngle}
Angle of repose of Kilobots controlled by light.
}
\end{figure}

%\textcolor{red}{TODO: Shiva will insert the kilobot images and a couple of sentences, and a couple of sentences about kilobots}

### 2018-09-10 ICRA19/intro.tex
added lead figure, and kilobot angle of repose section

 \begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{leadfigure.pdf}%\put(1,55){a)}
\end{overpic}
\caption{\label{fig:leadfigure} 
      \textcolor{blue}{TODO: we need a lead figure in column 1:   Combine kilobots from Fig 3 and 4 with photos of angle of repose by Haoran of iron with 4 rod angles. }
}
\end{figure}

>>>>

 \begin{figure}
\centering
\renewcommand{\figwid}{\columnwidth}
\begin{overpic}[width =\figwid]{firstpic.pdf}%\put(1,55){a)}
\end{overpic}
\caption{\label{fig:leadfigure} 
     Reshaping particles by collisions with rigid bodies. Top pictures illustrates using closed boundaries to reshape the particles. Bottom pictures illustrates angle of repose of different particles.
}
\end{figure}
